Nature Neuroscience Submission Letter

### 2019-09-06 paper/nature neuroscience submission/cover_letter.tex
updated cover letter

\begin{document}
\begin{newlfm}
  We have enclosed our manuscript entitled \textit{High-level
    cognition during story listening is reflected in high-order
    dynamic correlations in neural activity patterns}, which we wish
  to submit for publication as a Brief Communication in \textit{Nature
    Neuroscience}.

@@

  We have suggested the following scientists as expert reviewers:
  Richard Betzel (EMAIL), Danielle Bassett (EMAIL), Emily Finn
  (EMAIL), Olaf Sporns (EMAIL), and Christopher Honey (EMAIL).

  We note that we have included the complete methods section in the
  main text to facilitate peer review.  If deemed potentially suitable
  for publication, we will update our manuscript by moving the current
  methods section into our supporting document, and by adding a
  methods summary conforming to the Brief Communications format.
  Thank you for considering our manuscript for publication in Nature
  Neuroscience.

>>>>

\begin{document}
\begin{newlfm}
  We have enclosed our manuscript entitled \textit{High-level
    cognition during story listening is reflected in high-order
    dynamic correlations in neural activity patterns}, which we wish
  to submit for publication as an Article in \textit{Nature
    Neuroscience}.

@@

  We have suggested the following scientists as expert reviewers:
  Richard Betzel (r\-bet\-zel@in\-di\-ana.edu), Danielle Bassett (dsb@seas.upenn.edu), Emily Finn
  (emily.finn@nih.gov), Olaf Sporns (o\-sporns@in\-di\-ana.edu), and Christopher Honey (chris.honey@jhu.edu).

  We note that we have included the complete methods section in the
  main text to facilitate peer review.  If deemed potentially suitable
  for publication, we will update our manuscript by moving the current
  methods section into an \textit{Online methods} section in our
  supporting document.  Thank you for considering our manuscript for
  publication in Nature Neuroscience.
